\bf Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-08-19 doc/Response.Rmd

*Thank you for poining this out, you are right in your understanding of the method. We have changed figure 5 for clarification and expanded our discussion, which hopefully makes it easier to understand the method.*

- The results presented on page 14 list the correct identification of "same-source and difference-source toolmarks of 93.5 to 94.1%". Does this mean the true positives are 93.5% and the true negatives are 94.1%? I don't think so because the next sentence lists the false negative rate of between 0.28 and 0.36. The authors need to explicitly list the true positive rate and the true negative rate. These must be separate because there are many more true negatives than true positives in any matching dataset. That means that an algorithm that always predicts "different source" would be correct most of the time. In fact, for the author's dataset the "always predict different" algorithm would be correct approximately 94% of the time (35 bullets where each has appx 2 matches). The lack of a true positive rate and true negative rate is is a major point that must be corrected. To be clear, the true positive rate, true negative rate, false positive rate, and false negative rate should all be reported for the first dataset, perhaps added to Table 3 or another table like Table 3.

*Thank you for bringing this to our notice. We have indluded a paragraph with a definition of error rates, and switched to a table to show the results as suggested below.*

- The true positive rate, true negative rate, false positive rate, and false negative rate should also be presented for the second dataset (Hamby 44 scans, Sec 3.5). The authors do present AUC and EER curves but these are less informative and can often be used to hide weaker performing models.

*We have added a table with error rates for the Hamby 44 scans.*

- The results should all be listed as either fractions or all as percent (which is preferred) and not mix them.

@@

*We have changed the reporting to error percentages.*

- p21 the authors state "this kind of assessment is only feasible in the setting of a large study, such as the one we presented".  I strongly disagree with the use of the word "large". The presented work is not a large study. Ten firearms were used in each of two studies (it's not clear if both datasets used the same 10 firearms). A large study would include at least 100 different firearms and even 100 is not likely to provide statistical confidence. This is a very important point. If the paper is allowed to state that the described work is a large study it will set a precedent that will be detrimental to the field.

*We agree the data available to us is by no means large. Our comment was referring to the availability of 35 bullets rater than just 2 0r 3 as might be seen in actual case work. We have changed the sentence accordingly.*

### 2018-08-19 doc/paper.Rmd
last couple of comments addressed

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6-rescaled.pdf}
```{r, eval=FALSE, echo=FALSE, fig.width=8, fig.height=3, out.width='\\textwidth'}
land <- read.csv("../data/b6b2l6.csv")
land %>% ggplot(aes(x = y, y=resid)) +geom_line() +theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep="")))
```

@@

For both same- and different-shift pairs correlations between the  markings are calculated. 
The intuition here is that for two markings from the same-source the correlation for the in-phase sample should be high, while the correlations of the out-of-phase sample  provide a measure for the base-level correlation for non-matching marks of a given length $w_v$.
More specifically, the null hypothesis of the Chumbley score test is stated as **$H_o$: the markings come from two different sources** with the alternative given as **$H_a$: the markings come from the same source**. A $p$-value for the Chumbley score test is  then computed as a Mann Whitney U statistic to compare between in-phase sample and out-of-phase sample. A low $p$-value is  interpreted as a rejection of the null hypothesis in favor of the alternative hypothesis of `same-source`.

@@

We then define the pairs for different-shifts as
\begin{equation}\label{eq.diff2}
\left(s_{(j)}^{(1)}, s_{(I-j+1)}^{(1)} \right) \text{ for } j = 
\begin{cases}
1, ..., I & \text{ for even } I \\
1, ..., (I-1)/2, (I-1)/2 + 2, ..., I & \text{ for odd } I
\end{cases},
\end{equation}
i.e.\ for an odd number of same-shift correlations, we skip the middle pair for the different-shift correlations (see \autoref{sketch-diff-2}).
This pairing ensures that the number of different-shift pairings is the same or at most one less than the number of same-shift pairings in all tests.
In the remainder of the paper, we will refer to the algorithm defined by \citet{hadler} as \textbf{(CS1)} and the suggested modified algorithm as \textbf{(CS2)} and compare their performance on the available scans of the Hamby study.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[width=.7\textwidth]{images/sketch-diff-2.png}
\caption{\label{sketch-diff-2}Sketch of adjusted different-shift pairings. At most one of the same-shift pairings can not be matched with a different-shift pair under algorithm (CS2). }
\end{figure}

@@

\newpage
\subsection{Type 2 errors: CS1 vs CS2}
\label{appendix:appxtype2}
\autoref{fig:type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6-rescaled.png}
```{r, eval=FALSE, echo=FALSE, fig.width=8, fig.height=3, out.width='\\textwidth'}
land <- read.csv("../data/b6b2l6.csv")
land %>% ggplot(aes(x = y, y=resid)) +geom_line() +theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep="")))
```

@@

For both same- and different-shift pairs correlations between the  markings are calculated. 
The intuition here is that for two markings from the same-source the correlation for the in-phase sample should be high, while the correlations of the out-of-phase sample  provide a measure for the base-level correlation for non-matching marks of a given length $w_v$.
More specifically, the null hypothesis of the Chumbley score test is stated as **$H_o$: the markings come from two different sources** with the alternative given as **$H_a$: the markings come from the same source**. A $p$-value for the Chumbley score test is  then computed as a Mann Whitney U statistic to compare between in-phase sample and out-of-phase sample. A low $p$-value is  interpreted as a rejection of the null hypothesis in favor of the alternative hypothesis of *same-source*.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[width=.7\textwidth]{images/sketch-diff-2.png}
\caption{\label{sketch-diff-2}Sketch of adjusted different-shift pairings. Pairings are side from opposite ends of the two markings. For an odd number of pairings the middle pair is left out. At most one of the same-shift pairings can not be matched with a different-shift pair under algorithm (CS2). }
\end{figure}

We then define the pairs for different-shifts by matching up windows from opposite ends of the markings, i.e. the first pair consists of a matchup of the first window on the first marking and the last window on the second marking, the second pair consists of the second window on the first marking and the second to last pair on the second marking, and so on. In case of an odd number of pairs we need to be careful to exclude the middle pair from this assignment:  the middle pair is already part of the same-shift pair, therefore we cannot re-use the same pair as part of the different-shift pairs.

Mathematically,  this assignment of pairs is written as: 
\begin{equation}\label{eq.diff2}
\left(s_{(j)}^{(1)}, s_{(I-j+1)}^{(1)} \right) \text{ for } j = 
\begin{cases}
1, ..., I & \text{ for even } I \\
1, ..., (I-1)/2, (I-1)/2 + 2, ..., I & \text{ for odd } I
\end{cases}.
\end{equation}
Note that for an odd number of same-shift correlations, we skip the middle pair for the different-shift correlations (see also \autoref{sketch-diff-2}).
This pairing ensures that the number of different-shift pairings is the same or at most one less than the number of same-shift pairings in all tests.
In the remainder of the paper, we will refer to the algorithm defined by \citet{hadler} as \textbf{(CS1)} and the suggested modified algorithm as \textbf{(CS2)} and compare their performance on the available scans of the Hamby study.

@@

@@

\subsection{Type 2 errors: CS1 vs CS2}
\label{appendix:appxtype2}
\autoref{fig:type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

### 2018-08-19 doc/paper.tex
last couple of comments addressed

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
%\usepackage[numbers]{natbib}
\usepackage{natbib}
\setcitestyle{numbers} 
\makeatletter % Reference list option change
\renewcommand\@biblabel[1]{#1. } % from [1] to 1
\makeatother %

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6-rescaled.pdf}

@@

For both same- and different-shift pairs correlations between the
markings are calculated. The intuition here is that for two markings
from the same-source the correlation for the in-phase sample should be
high, while the correlations of the out-of-phase sample provide a
measure for the base-level correlation for non-matching marks of a given
length \(w_v\). More specifically, the null hypothesis of the Chumbley
score test is stated as \textbf{\(H_o\): the markings come from two
different sources} with the alternative given as \textbf{\(H_a\): the
markings come from the same source}. A \(p\)-value for the Chumbley
score test is then computed as a Mann Whitney U statistic to compare
between in-phase sample and out-of-phase sample. A low \(p\)-value is
interpreted as a rejection of the null hypothesis in favor of the
alternative hypothesis of \texttt{same-source}.

@@

We then define the pairs for different-shifts as
\begin{equation}\label{eq.diff2}
\left(s_{(j)}^{(1)}, s_{(I-j+1)}^{(1)} \right) \text{ for } j = 
\begin{cases}
1, ..., I & \text{ for even } I \\
1, ..., (I-1)/2, (I-1)/2 + 2, ..., I & \text{ for odd } I
\end{cases},
\end{equation} i.e.~for an odd number of same-shift correlations, we
skip the middle pair for the different-shift correlations (see
\autoref{sketch-diff-2}). This pairing ensures that the number of
different-shift pairings is the same or at most one less than the number
of same-shift pairings in all tests. In the remainder of the paper, we
will refer to the algorithm defined by \citet{hadler} as \textbf{(CS1)}
and the suggested modified algorithm as \textbf{(CS2)} and compare their
performance on the available scans of the Hamby study.

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
%\usepackage[numbers]{natbib}
\usepackage[nomarkers]{endfloat}
\usepackage{natbib}
\setcitestyle{numbers} 
\makeatletter % Reference list option change
\renewcommand\@biblabel[1]{#1. } % from [1] to 1
\makeatother %

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6-rescaled.png}

@@

For both same- and different-shift pairs correlations between the
markings are calculated. The intuition here is that for two markings
from the same-source the correlation for the in-phase sample should be
high, while the correlations of the out-of-phase sample provide a
measure for the base-level correlation for non-matching marks of a given
length \(w_v\). More specifically, the null hypothesis of the Chumbley
score test is stated as \textbf{\(H_o\): the markings come from two
different sources} with the alternative given as \textbf{\(H_a\): the
markings come from the same source}. A \(p\)-value for the Chumbley
score test is then computed as a Mann Whitney U statistic to compare
between in-phase sample and out-of-phase sample. A low \(p\)-value is
interpreted as a rejection of the null hypothesis in favor of the
alternative hypothesis of \emph{same-source}.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[width=.7\textwidth]{images/sketch-diff-2.png}
\caption{\label{sketch-diff-2}Sketch of adjusted different-shift pairings. Pairings are side from opposite ends of the two markings. For an odd number of pairings the middle pair is left out. At most one of the same-shift pairings can not be matched with a different-shift pair under algorithm (CS2). }
\end{figure}

We then define the pairs for different-shifts by matching up windows
from opposite ends of the markings, i.e.~the first pair consists of a
matchup of the first window on the first marking and the last window on
the second marking, the second pair consists of the second window on the
first marking and the second to last pair on the second marking, and so
on. In case of an odd number of pairs we need to be careful to exclude
the middle pair from this assignment: the middle pair is already part of
the same-shift pair, therefore we cannot re-use the same pair as part of
the different-shift pairs.

Mathematically, this assignment of pairs is written as:
\begin{equation}\label{eq.diff2}
\left(s_{(j)}^{(1)}, s_{(I-j+1)}^{(1)} \right) \text{ for } j = 
\begin{cases}
1, ..., I & \text{ for even } I \\
1, ..., (I-1)/2, (I-1)/2 + 2, ..., I & \text{ for odd } I
\end{cases}.
\end{equation} Note that for an odd number of same-shift correlations,
we skip the middle pair for the different-shift correlations (see also
\autoref{sketch-diff-2}). This pairing ensures that the number of
different-shift pairings is the same or at most one less than the number
of same-shift pairings in all tests. In the remainder of the paper, we
will refer to the algorithm defined by \citet{hadler} as \textbf{(CS1)}
and the suggested modified algorithm as \textbf{(CS2)} and compare their
performance on the available scans of the Hamby study.
